Continuous Generalization of Buildings \\ by Growing and Aggregating

### 2017-09-14 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
removed tiny edges after growing
added figures/NearestPoints.pdf

These methods are interesting but only work on lines and our problem of 
building polygon interpolation cannot be achieved by similar morphings. 
Regarding the continuous generalization of polygon map features,
\citet{Danciger2009} proposed to grow polygons when a map was zoomed out. Their 
method 
preserves polygons' topology, area-ratios, and relative positions.  In the case 
where the goal map is an aggregated version of start landcover map, 
\citet{Peng2017_AStar} computed optimal aggregation sequences for land-cover 
areas.

@@

\subsection{Aggregating close buildings by introducing bridges}
\label{sec:Merge}

If a group of buildings will become too close at time $t$ because of growing,
we aggregate the original buildings by introducing bridges, 
then we grow the bridged building (see \fig\ref{fig:GrowAndBridge}).
We show how to group buildings for time $t$ in \sect\ref{sec:Group}.
No matter a bridge appears earlier or later, 
it has width $2\dtrm{G}$ at time $t$.
This setting guarantees that no bridge is thin when $t=1$.

@@

For each pair of buildings in the same group, 
we find a nearest pair of points.
We connect the buildings by adding a line segment bridging the nearest points.
If we consider each building as a node and each line segment as an edge, 
then we have a graph.
Using Prim's algorithm \citep{Prim1957}, 
we find a minimum spanning tree (MST) in the graph
taking the lengths of the line segments as the weights.
As a results, the line segments corresponding to the edges in the MST
are used as bridges to aggregate the buildings.

@@

Original buildings grow according to time $t$.
We put the original buildings in the same group if 
they grow to become too close.
We group buildings based on buffering.
The basic idea is that 
we buffer the original buildings with distance $\dtrm{G}$
and an additional distance $\dtrm{C}$.
We will talk about how to define $\dtrm{C}$ later.
If two buffers overlap, 
then the original buildings are put in the same group.

>>>>

These methods are interesting but only work on lines and our problem of 
building polygon interpolation cannot be achieved by similar morphings. 
Regarding the continuous generalization of polygon map features,
\citet{Danciger2009} proposed to grow polygons when a map was zoomed out. Their 
method 
preserves polygons' topology, area-ratios, and relative positions.  In the case 
where the goal map is an aggregated version of start land-cover map, 
\citet{Peng2017_AStar} computed optimal aggregation sequences for land-cover 
areas.

@@

\subsection{Aggregating close buildings by adding bridges}
\label{sec:Merge}

We aggregate buildings if they become too close because of growing.
Our basic idea is to add bridges between buildings
(see for example \fig\ref{fig:GrowAndBridge}).

@@

At time $t=1$, we know that 
which buildings will finally be aggregated into the same built-up area
(see \sect\ref{sec:Group}).
We connect each pair of these buildings by adding a line segment linking the 
nearest points.
If we consider each building as a node and each line segment as an edge, 
then we have a graph.
Using Prim's algorithm \citep{Prim1957}, 
we find a minimum spanning tree (MST) in the graph,
taking the lengths of the line segments as the weights.
As a results, the line segments corresponding to the edges in the MST
are used as bridges.
At any time $t$, we pick some of the bridges to aggregate the buildings.
Then we grow the bridged buildings (see \fig\ref{fig:GrowAndBridge}).
No matter a bridge appears earlier or later, 
it has width $2\dtrm{G}$ at time $t$.
This setting guarantees that no bridge is thin when $t=1$.
We do not introduce bridges according to nearest points at time $t$
because the nearest points may change (see \fig\ref{fig:NearestPoints} for 
example).

\begin{figure}[tb]
	\centering
	\includegraphics[]{NearestPoints}
	\caption{The nearest points between a pair of buildings may change because 
	of growing. 
		The two squares and the two circles respectively mark
		the nearest points before and after growing.
	}
	\label{fig:NearestPoints}
\end{figure}

@@

Original buildings grow according to time $t$.
We put the original buildings in the same group if 
they grow to become too close.
We group buildings based on buffering.
The basic idea is that 
we buffer the original buildings with distance $\dtrm{G}$
and an additional distance $\dtrm{C}$
(We will talk about how to define $\dtrm{C}$ later).
If two buffers overlap, 
then the original buildings are put in the same group.
